### 2015-10-26 analysis/index.Rmd
added plotting Rmd files
add more figure plotting rmd files; tidy up size and cropping of pdf
add more figures

@@

>>>>

## Simple illustrations

*  [Illustrate Zero Assumption](makefig_FDReg.html)
*  [Illustatrate dilution effect of low-precision observations](make_GOODPOOR_figs.html)

@@

*  [Plot Densities of simulations](plot_egdens.html)
*  [Plot estimates of pi0](plot_pi0est.html)
*  [Plot local false sign rates and lfdr vs truth](plot_lfsr.html)
*  [Plot CDFs](plot_cdf_eg.html)

### 2015-10-26 paper/main.tex
add more figures

\begin{figure}
\center \includegraphics[height=6in]{figures/decomp_ZA.pdf}
\caption{Illustration that the unimodal assumption (UA) in \ashr can produce very different results from existing methods.
The figure shows, for a single simulated dataset, the way different methods decompose $p$ values (left) and $z$ scores (right) into a null component (dark blue) and an alternative component (cyan). In the $z$ score space the alternative distribution is placed on the bottom to highlight the differences in its shape among methods.
The three existing methods (\qvalue, \locfdr, \mixfdr) all effectively make the Zero Assumption, which results in a ``hole" in the alternative $z$ score distribution around 0.
In contrast the method introduced here (\ashr) makes the Unimodal Assumption -- that the effect sizes, and thus the $z$ scores, have a unimodal distribution about 0 -- which yields a very different decomposition. (In this case the \ashr decomposition is closer to the truth: the data were simulated under a model where all of the effects are non-zero, so the ``true" decomposition would make everything cyan.)} \label{fig:ZA}
\end{figure}

@@

\begin{figure}
\begin{subfigure}{\textwidth}
\centering\includegraphics[width=4in]{figures/GOODPOOReg_hist.pdf} 
    \label{fig:goodpoor-hist}
    \caption{Density histograms of $p$ values for good-precision, poor-precision, and combined observations}
 \end{subfigure}
\begin{subfigure}{\textwidth}
\centering\includegraphics[width=4in]{figures/GOODPOOReg_scatter.pdf}
    \caption{Comparison of results of different methods applied to good-precision observations only ($x$ axis) and combined data ($y$ axis). Each point shows the ``significance" ($q$ values from \qvalue; $\lfdr$ for \locfdr; $\lfsr$ for \ashr) of a good-precision observation under the two different analyses.} \label{fig:goodpoor-scatter}
\end{subfigure}
\caption{Simulation illustrating how, for existing FDR methods, 
poor-precision observations can contaminate signal from good-precision observations. The top panel (a) illustrates that when 
$p$ values from good-precision observations (left) and from poor-precision observations (center) are combined (right), they produce
a distribution of $p$ values with less overall signal - and so, by conventional methods, will give a higher estimated FDR at any given threshold.
The bottom panel (b) illustrates this behaviour directly for the methods \qvalue and \locfdr: the $q$-values from \qvalue and the $\lfdr$ estimates from \locfdr are higher when applied to all data than when applied to good-precision observations only. In contrast the methods described here (\ashr) produce effectively the same results (here, the lfsr) in the good-precision and combined data analyses.} \label{fig:goodpoor}
\end{figure}

@@

\begin{figure}
\centering\includegraphics[width=4in]{figures/lfsr_vs_pval_GOODPOOR.pdf}
\caption{Figure illustrating affects of prior assumptions on re-ordering of significance. Left panel shows results under our ``default prior" which assumes that effects $\beta_j$ are identically distributed, independent of $s_j$. Right panel shows results under the ``$p$-value prior", which assumes that $z$ scores $\beta_j/s_j$ are identically distributed, independent of $s_j$.} \label{fig:lfsr_pval}
\end{figure}

>>>>

\begin{figure}
\center \includegraphics[height=6in]{../analysis/figure/makefig_FDReg.Rmd/decomp_ZA-1.pdf}
\caption{Illustration that the unimodal assumption (UA) in \ashr can produce very different results from existing methods.
The figure shows, for a single simulated dataset, the way different methods decompose $p$ values (left) and $z$ scores (right) into a null component (dark blue) and an alternative component (cyan). In the $z$ score space the alternative distribution is placed on the bottom to highlight the differences in its shape among methods.
The three existing methods (\qvalue, \locfdr, \mixfdr) all effectively make the Zero Assumption, which results in a ``hole" in the alternative $z$ score distribution around 0.
In contrast the method introduced here (\ashr) makes the Unimodal Assumption -- that the effect sizes, and thus the $z$ scores, have a unimodal distribution about 0 -- which yields a very different decomposition. (In this case the \ashr decomposition is closer to the truth: the data were simulated under a model where all of the effects are non-zero, so the ``true" decomposition would make everything cyan.)} \label{fig:ZA}
\end{figure}

@@

\begin{figure}
\begin{subfigure}{\textwidth}
\centering\includegraphics[width=4in]{../analysis/figure/make_GOODPOOR_figs.Rmd/GOODPOOReg_hist-1.pdf} 
    \label{fig:goodpoor-hist}
    \caption{Density histograms of $p$ values for good-precision, poor-precision, and combined observations}
 \end{subfigure}
\begin{subfigure}{\textwidth}
\centering\includegraphics[width=4in]{../analysis/figure/make_GOODPOOR_figs.Rmd/GOODPOOReg_scatter-1.pdf}
    \caption{Comparison of results of different methods applied to good-precision observations only ($x$ axis) and combined data ($y$ axis). Each point shows the ``significance" ($q$ values from \qvalue; $\lfdr$ for \locfdr; $\lfsr$ for \ashr) of a good-precision observation under the two different analyses.} \label{fig:goodpoor-scatter}
\end{subfigure}
\caption{Simulation illustrating how, for existing FDR methods, 
poor-precision observations can contaminate signal from good-precision observations. The top panel (a) illustrates that when 
$p$ values from good-precision observations (left) and from poor-precision observations (center) are combined (right), they produce
a distribution of $p$ values with less overall signal - and so, by conventional methods, will give a higher estimated FDR at any given threshold.
The bottom panel (b) illustrates this behaviour directly for the methods \qvalue and \locfdr: the $q$-values from \qvalue and the $\lfdr$ estimates from \locfdr are higher when applied to all data than when applied to good-precision observations only. In contrast the methods described here (\ashr) produce effectively the same results (here, the lfsr) in the good-precision and combined data analyses.} \label{fig:goodpoor}
\end{figure}

@@

\begin{figure}
\centering\includegraphics[width=4in]{../analysis/figure/make_GOODPOOR_figs.Rmd/lfsr_vs_pval_GOODPOOR-1.pdf}
\caption{Figure illustrating affects of prior assumptions on re-ordering of significance. Left panel shows results under our ``default prior" which assumes that effects $\beta_j$ are identically distributed, independent of $s_j$. Right panel shows results under the ``$p$-value prior", which assumes that $z$ scores $\beta_j/s_j$ are identically distributed, independent of $s_j$.} \label{fig:lfsr_pval}
\end{figure}
